---
title: "House Price Prediction"
author: "Kiana Toufighi"
date: "18 October 2016"
output: 
  html_document:
    toc: TRUE
    number_sections: TRUE
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction 

This is a first attempt at exploring a dataset which a XX features in order to predict price.  I will attempt to use linear regression for modelling these data in the first iteration and more and more advanced techniques only as needed. 


## Library Loading

You can also embed plots, for example:

```{r libraries, results = 'hide', message = FALSE, warning = FALSE}
library(ggplot2)
library(ggthemes)
library(randomForest)
library(Amelia)

```


# Data Wrangling

In this section we load data, familiarise ourselves with the data, examine missing features, and look at how to imputate missing values. 

## Data Loading

```{r data, results = FALSE}

# build absolute path for loading data files
path <- file.path("/Users", Sys.info()["user"], "Dropbox (Personal)/Script Repository/R/Kaggle/HousePrices")
train <- read.csv(file.path(path, "data/train.csv"), header = TRUE, na.strings = c("", NA))
test <- read.csv(file.path(path, "data/test.csv"), header = TRUE)
whole <- rbind(train[,-81], test)


# examine missing values in dataset
missmap(whole, col = c("yellow", "blue"), x.cex = 0.6)
```

With a single glance we see that the top five features missing most of their values are: PoolQC, MiscFeatures, Alley, Fence, and FireplaceQu. What we can impute however are all features that have to do with Garage and Basement. 
```{r some_plots, echo = FALSE}

# look at price range (IQR) within each neighbourhood
ggplot(train, aes(x = as.factor(Neighborhood), y = SalePrice)) +
  geom_boxplot() +
  labs(title = "Sale Price by Neighbourhood", x = "Neighbourhood", y = "Sale Price") +
  scale_x_discrete(labels = abbreviate) +
  theme_bw()


```

# Feature Engineering 

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
